The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging with the Owens Valley Long Wavelength Array

### 2017-07-05 paper.tex
use aastex features

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{natbib}

@@

\begin{figure*}[ht]
    \includegraphics[width=\textwidth]{maps/rgb-map-small}
    \caption{three color map}
    \label{fig:rgb}
\end{figure*}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=\columnwidth]{figures/lcurve/lcurve}
    \caption{
        Example l-curve (from spw04)
    }
    \label{fig:lcurve}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=\columnwidth]{figures/antenna-layout/antenna-layout}
    \caption{
        This figure shows the antenna layout for the OVRO-LWA. Black dots correspond to antennas
        within the 200 m diameter core of the array. The 32 open circles are the expansion antennas
        built in early 2016 in order to increase the longest baseline to 1.5 km. The 5 crosses are
        antennas equipped with noise-switched front ends.
    }
    \label{fig:antenna-layout}
\end{figure}

@@

\begin{figure*}[ht]
    \gridline{
        \fig{figures/beam/source-tracks}{0.45\textwidth}{(a)}
        \fig{figures/beam/stokes-I-beam}{0.45\textwidth}{(b)}
    }
    \caption{
        Example beam model (from spw04).
    }
    \label{fig:beam}
\end{figure*}

@@

We measure the flux of several bright sources (Cyg A, Cas A, Tau A, Vir A, Her A, Hya A, Per B, and
3C 353) as they pass through the sky and then fit a beam model composed of Zernike polynomials to
those flux measurements. We select the basis functions to have the desired symmetry ($Z_0^0$,
$Z_2^0$, $Z_4^0$, $Z_4^4$, $Z_6^0$, $Z_6^4$, $Z_8^0$, $Z_8^4$, $Z_8^8$) and the beam amplitude at
zenith is constrained to be unity.

\todo{plot that shows the tracks after symmetries applied and the resulting beam fit?}

@@

\begin{figure*}[ht]
    \centering
    \begin{tabular}{cccc}
        \includegraphics[width=0.22\textwidth]{figures/smeared-images/before-component-removal-spw14} &
        \includegraphics[width=0.22\textwidth]{figures/smeared-images/after-component-removal-spw14} &
        \includegraphics[width=0.22\textwidth]{figures/smeared-images/rfi-like-component-spw14} &
        \includegraphics[width=0.22\textwidth]{figures/smeared-images/pickup-like-component-spw14} \\
        \textbf{(a)} & \textbf{(b)} & \textbf{(c)} & \textbf{(d)} \\
    \end{tabular}
    \caption{
        This figure illustrates the process of fitting for terrestrial sources of correlated noise.
        Each image is of the entire visible hemisphere above the OVRO-LWA but the data has been
        averaged over the entire 28 hour observing period. Because of this Cas A and Cyg A are
        smeared along tracks of constant declination. These images are generated using WSCLEAN
        \citep{2014MNRAS.444..606O}, uniform weighting, and baselines shorter than 15 wavelengths
        are flagged. \textbf{(a)} This image shows the initial data before any sources have been
        removed. \textbf{(b)} This image shows the final state after 3 terrestrial sources of
        correlated noise have been removed. \textbf{(c)} This image illustrates the contribution of
        an RFI source towards the north-west that was removed by peeling. \textbf{(d)} This removed
        component is not associated with a dot on the horizon.  Instead it is likely associated with
        common-mode pickup in the analog signal chain.
    }
    \label{fig:fitrfi}
\end{figure*}

@@

%\begin{figure*}[ht]
%    \centering
%    \begin{tabular}{cc}
%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
%    \end{tabular}
%    \caption{single channel maps}
%\end{figure*}
%
%\begin{figure*}[ht]
%    \centering
%    \begin{tabular}{cc}
%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} &
%        \includegraphics[width=\columnwidth, draft]{maps/rgb-map} \\
%    \end{tabular}
%    \caption{jackknifed error maps}
%\end{figure*}

\begin{table*}[t]
    \centering
    \begin{tabular}{ccccc}
        \hline\hline
        \# & $\nu$ / MHz & $\Delta\nu$ / MHz
           & $\theta$ / arcmin  & noise / Jy \\ \hline
        1 & 36.528 & 0.024 & & \\
        2 & 41.760 & 0.024 & & \\
        3 & 46.992 & 0.024 & & \\
        4 & 52.224 & 0.024 & & \\
        5 & 57.456 & 0.024 & & \\
        6 & 62.688 & 0.024 & & \\
        7 & 67.920 & 0.024 & & \\
        8 & 73.152 & 0.024 & & \\
        \hline\hline
    \end{tabular}
    \caption{Summary of the produced maps}
\end{table*}

>>>>

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}

@@

\begin{figure*}[ht]
    \plotone{maps/rgb-map-small}
    \caption{three color map}
    \label{fig:rgb}
\end{figure*}

@@

\begin{figure}[t]
    \plotone{figures/lcurve/lcurve}
    \caption{
        Example l-curve (from spw04)
    }
    \label{fig:lcurve}
\end{figure}

@@

\begin{figure}[t]
    \plotone{figures/antenna-layout/antenna-layout}
    \caption{
        This figure shows the antenna layout for the OVRO-LWA. Black dots correspond to antennas
        within the 200 m diameter core of the array. The 32 open circles are the expansion antennas
        built in early 2016 in order to increase the longest baseline to 1.5 km. The 5 crosses are
        antennas equipped with noise-switched front ends.
    }
    \label{fig:antenna-layout}
\end{figure}

@@

\begin{figure*}[ht]
    \plottwo{figures/beam/source-tracks}{figures/beam/stokes-I-beam}
    \caption{
        Example Stokes-I beam model (from spw04).
    }
    \label{fig:beam}
\end{figure*}

@@

We measure the flux of several bright sources (Cyg A, Cas A, Tau A, Vir A, Her A, Hya A, Per B, and
3C 353) as they pass through the sky and then fit a beam model composed of Zernike polynomials to
those flux measurements. We select the basis functions to have the desired symmetry ($Z_0^0$,
$Z_2^0$, $Z_4^0$, $Z_4^4$, $Z_6^0$, $Z_6^4$, $Z_8^0$, $Z_8^4$, $Z_8^8$) and the beam amplitude at
zenith is constrained to be unity. See Figure~\ref{fig:beam} for an illustration of the fitted beam
model.

@@

\begin{figure*}[ht]
    \gridline{
        \fig{figures/smeared-images/before-component-removal-spw14}{0.22\textwidth}{(a)}
        \fig{figures/smeared-images/after-component-removal-spw14}{0.22\textwidth}{(b)}
        \fig{figures/smeared-images/rfi-like-component-spw14}{0.22\textwidth}{(c)}
        \fig{figures/smeared-images/pickup-like-component-spw14}{0.22\textwidth}{(d)}
    }
    \caption{
        This figure illustrates the process of fitting for terrestrial sources of correlated noise.
        Each image is of the entire visible hemisphere above the OVRO-LWA but the data has been
        averaged over the entire 28 hour observing period. Because of this Cas A and Cyg A are
        smeared along tracks of constant declination. These images are generated using WSCLEAN
        \citep{2014MNRAS.444..606O}, uniform weighting, and baselines shorter than 15 wavelengths
        are flagged. \textbf{(a)} This image shows the initial data before any sources have been
        removed. \textbf{(b)} This image shows the final state after 3 terrestrial sources of
        correlated noise have been removed. \textbf{(c)} This image illustrates the contribution of
        an RFI source towards the north-west that was removed by peeling. \textbf{(d)} This removed
        component is not associated with a dot on the horizon.  Instead it is likely associated with
        common-mode pickup in the analog signal chain.
    }
    \label{fig:fitrfi}
\end{figure*}

@@

\floattable
\begin{deluxetable}{ccccc}
    \tablecaption{Summary of the produced maps\label{tab:summary}}
    \tablehead{
        \colhead{\#} & \colhead{$\nu$ / MHz} & \colhead{$\Delta\nu$ / MHz} &
        \colhead{$\theta$ / arcmin} & \colhead{noise / Jy}
    }
    \startdata
        1 & 36.528 & 0.024 & & \\
        2 & 41.760 & 0.024 & & \\
        3 & 46.992 & 0.024 & & \\
        4 & 52.224 & 0.024 & & \\
        5 & 57.456 & 0.024 & & \\
        6 & 62.688 & 0.024 & & \\
        7 & 67.920 & 0.024 & & \\
        8 & 73.152 & 0.024 & & \\
    \enddata
\end{deluxetable}
